Figures

### 2020-03-13 manuscript/figures.Rmd
caption adjustments

\arrayrulecolor{white}
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 6, dev = c("pdf"))
knitr::opts_chunk$set(fig.pos = 'H')
```

@@

![Diagram showing the assumption of most lake depth models that the nearshore slope is extends into the lake and that all lakes have a common relationship between nearshore and in-lake slope. ](../figures/slope_diagram.pdf){width=75%}

@@

```{r lgnemanual-vs-bathy-depth, fig.cap="Comparison between reported depth and depth calculated from bathymetry surfaces.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra=''}
# see 00_qa.Rmd
knitr::include_graphics("../figures/lgnemanual-vs-bathy-depth-1.pdf")
```

>>>>

\arrayrulecolor{white}
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", dev = c("pdf"))
knitr::opts_chunk$set(fig.pos = 'H')
```

@@

![Diagram showing the assumption of most lake depth models that the nearshore slope extends into the lake and that all lakes have a common relationship between nearshore and in-lake slope. ](../figures/slope_diagram.pdf){width=75%}

@@

```{r lgnemanual-vs-bathy-depth, fig.cap="Comparison between reported depth and depth calculated from bathymetry surfaces by US State.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra=''}
# see 00_qa.Rmd
knitr::include_graphics("../figures/lgnemanual-vs-bathy-depth-1.pdf")
```
